Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-29 doc/paper.tex
updates results

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%                    & 10\%                   & 20\%                  & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                    & 42.2                   & 51.09                  & 58.23                 & 59.23                  & 62.17                  & 67.43                  \\
            \hline
            PointContrast              & 44.79 \textbf{(+2.59)} & 55.28 \textbf{(+4.19)} & 57.98 (-0.25)         & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          \\
            Contrastive Scene Contexts & 42.6 \textbf{(+0.4)}   & 53.03 \textbf{(+1.94)} & 57.28 (-0.95)         & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} \\
            CME \textbf{(Ours)}        & 44.04 \textbf{(+1.84)} & 52.97 \textbf{(+1.88)} & 58.6 \textbf{(+0.37)} & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%  & 10\% & 20\%        & 30\%        & 40\%        & 100\%       \\
            \hline
            Scratch                    & 26.9 & 31.1 & 40.7        & 42.2        & 45.7        & 49.0        \\
            \hline
            PointContrast              &      & 35.3 & 40.5 (-0.2) & 43.0 (+0.8) & 43.9 (-1.8) & 49.1 (+0.1) \\
            Contrastive Scene Contexts &      & 35.5 & 41.6 (+0.9) & 42.9 (+0.7) & 44.6 (-1.1) & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        &      & 35.5 & 39.1 (-1.6) & 42.4 (+0.2) & 43.6 (-2.1) & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{0.3\textwidth}{!}{
        \begin{tabular}{ c | c }
                                       & mIOU  \\
            \hline
            Scratch                    & 41.82 \\
            \hline
            PointContrast              & 38.67 \\
            Contrastive Scene Contexts & 41.12 \\
            CME \textbf{(Ours)}        & 40.37 \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet & S3DIS & SunRGBD \\
            \hline
            Scratch                    & 35.2    &       & 32.0    \\
            \hline
            PointContrast              & 36.7    &       & 34.2    \\
            Contrastive Scene Contexts & 36.1    &       & 33.2    \\
            CME \textbf{(Ours)}        & 37.7    &       & 33.1    \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                                      & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                                   & 42.2                   & 51.09                  & 58.23                  & 59.23                  & 62.17                  & 67.43                  \\
            \hline
            PointContrast                             & 44.79 \textbf{(+2.59)} & 55.28 \textbf{(+4.19)} & 57.98 (-0.25)          & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          \\
            Contrastive Scene Contexts                & 42.6 \textbf{(+0.4)}   & 53.03 \textbf{(+1.94)} & 57.28 (-0.95)          & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} \\
            Contrastive Scene Contexts - 70\% overlap & 45.44 \textbf{(+3.24)} & 50.84 (-0.25)          & 59.26 \textbf{(+1.03)} & 59.72 \textbf{(+0.49)} & 62.72 \textbf{(+0.55)} & 68.01 \textbf{(+0.58)} \\
            Contrastive Scene Contexts - same scan    & 44.09 \textbf{(+1.89)} & 50.88 (-0.21)          & 56.64 (-1.59)          & 58.9 (-0.33)           & 61.50 (-0.67)          & 67.37 (-0.06)          \\
            CME \textbf{(Ours)}                       & 44.04 \textbf{(+1.84)} & 52.97 \textbf{(+1.88)} & 58.6 \textbf{(+0.37)}  & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%         & 10\% & 20\%        & 30\%        & 40\%        & 100\%       \\
            \hline
            Scratch                    & 26.9        & 31.1 & 40.7        & 42.2        & 45.7        & 49.0        \\
            \hline
            PointContrast              & 27.0 (+0.1) & 35.3 & 40.5 (-0.2) & 43.0 (+0.8) & 43.9 (-1.8) & 49.1 (+0.1) \\
            Contrastive Scene Contexts & 29.8 (+2.9) & 35.5 & 41.6 (+0.9) & 42.9 (+0.7) & 44.6 (-1.1) & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        & 25.5 (-1.4) & 35.5 & 39.1 (-1.6) & 42.4 (+0.2) & 43.6 (-2.1) & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                       & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                 \\
            \hline
            Scratch                    & 39.2                   & 40.43                  & 41.06                  & 41.67                  & 40.79                  & 41.01                 \\
            \hline
            PointContrast              & 40.29 \textbf{(1.09)}  & 42.59 \textbf{(+2.16)} & 42.2  \textbf{(+1.14)} & 41.65 (-0.02)          & 42.99 \textbf{(+2.2)}  &                       \\
            Contrastive Scene Contexts & 40.6 \textbf{(+1.4)}   & 42.21 \textbf{(+1.78)} & 42.26 \textbf{(+1.2)}  & 42.24 \textbf{(+0.57)} & 44.29 \textbf{(+3.5)}  & 43.01 \textbf{(+2.0)} \\
            CME \textbf{(Ours)}        & 39.49 \textbf{(+0.29)} & 40.90 \textbf{(+0.47)} & 40.91 (-0.15)          & 41.82 \textbf{(+0.15)} & 41.77 \textbf{(+0.98)} &                       \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}
